---
title: "STAT295"
author: "Başak Uğurlu"
date: "2024-04-15"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Intro to R Markdown

## R Markdown

This is an `R Markdown` document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r cars 2}
summary(cars)
```

# hello

you can embed plots

```{r press, echo=FALSE}
plot(pressure)

```

1.  l

2.  k

3.  m

4.  cute

### Format

superscript: 2^nd^

subscript: CO~2~

strike through: ~~mistake~~

```{r read-gapminder,eval=FALSE,echo=FALSE}
gap<-read.csv("gapminder.csv")
```

### code chunk options

```{r,warning=FALSE,include=TRUE,echo=FALSE}
sqrt(-1)
data <- CO2

```

### inline codes

adding inline codes `r sqrt(25)` and `r nrow(data)` and `r ncol(data)` , variables are \`r names(data)

## Tables

| Col1 | Col2 | Col3 |
|------|------|------|
|      |      |      |
|      |      |      |
|      |      |      |

: captioncaptioncaption

```{r mytable1}

top<-head(CO2)
knitr::kable(CO2)
knitr::kable(top,
             caption="captioncaption")
```

to cite a table we can use [Table\@ref](mailto:Table@ref){.email}(tab:mytable1)
